---
title: "presentation"
format: revealjs
editor: visual
---

# Welcome to Group 20's Presentation

## Who are we?

::::: columns
::: {.column width="50%"}
-   Joel
-   Hector
:::

::: {.column width="50%"}
-   Selene
-   Wes
:::
:::::

## Grocery Math

Let's begin with the basics and print our our result. If Bob needs ten apples and they cost \$2 each. How much money should Bob take to the grocery store?

```{r echo=TRUE}
num_apples <- 10
cost_apples <- 2
total <- num_apples * cost_apples

print(paste("Bob needs to take", total, "dollars with him."))
```

## Time to Exercise!

It's squats day - let's see how many reps you'll be doing!

```{r echo=TRUE}
exercise <- "squats"

if (exercise == "lunges") {
  reps <- 10
} else if (exercise == "pushups") {
  reps <- 15
} else if (exercise == "squats") {
  reps <- 25
} 

if (is.numeric(reps)) {
  print(paste("You must to do", reps, "reps of", exercise))
} else {
  print("You're lucky! Take a break!")
}
```

# How to do School

1.  Eat
2.  Study
3.  Sleep
4.  Repeat

# Keep on Trying

A person who never made a mistake never tried anything new. By: Albert Einstein
